### 2016-05-09 sec1_introduction.tex
Further edits on Sec1 and sec4

A crucial task of data analysis on top of trajectories is 
to discover co-moving patterns. A \emph{co-movement} pattern~\cite{li2013managing} 
refers to a group of objects traveling together for a certain period of time 
and the group is normally determined according to spatial proximity. 
A pattern is prominent if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$ are parameters specified by users. Rooted from such basic definition 
and driven by different mining applications, there are a bunch of variants 
of co-moving patterns that have been developed with more advanced constraints.

Table~\ref{tbl:existing_co_patterns} summarizes several popular co-moving patterns 
with different constraints in the attributes of clustering method and length of temporal duration. 
In particular,  the \emph{flock}~\cite{gudmundsson2006flock} 
and \emph{group}~\cite{wang2006grouppattern} patterns require 
all the objects in a group to be enclosed by a disk with radius $r$; 
whereas the \emph{convoy}~\cite{jeung2008convoy}, \emph{swarm}~\cite{li2010swarm} 
and \emph{platoon}~\cite{li2015platoon} patterns adopt density-based 
spatial clustering in determining groups. 
In the temporal dimension, \emph{flock}~\cite{gudmundsson2006flock} 
and \emph{convoy}~\cite{jeung2008convoy} require all the timestamps 
of each detected spatial group to be consecutive, which was referred to as \emph{global consecutiveness}; 
whereas \emph{swarm}~\cite{li2010swarm} does not impose any restriction. 
The \emph{group}~\cite{wang2006grouppattern} and \emph{platoon}~\cite{li2015platoon} use a compromised manner and allow gaps between the consecutive segments, which was referred to as \emph{local consecutiveness}. 
They introduce a parameter $L$ to control the minimum length of each local consecutive segment.

@@

\begin{table} \scriptsize
\centering
\begin{tabular}{|c|c|c|c|}
\hline 
 & Spatial Proximity & Consecutiveness &  Time Complexity\\ 
\hline 
flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||T|^2 + |\mathbb{O}|log(|\mathbb{O}|))$ \\ 
\hline 
convoy~\cite{jeung2008convoy} & density-based &   global & $O(|T|^2+|\mathbb{O}||T|)$\\ 
\hline 
group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|T|)$ \\ 
\hline 
swarm~\cite{li2010swarm} & density-based  & no constraint & $O(2^{|\mathbb{O}|}|\mathbb{O}||T|)$  \\ 
\hline 
platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||T|)$\\ 
\hline 
\end{tabular} 
\caption{Existing co-movement patterns. The time complexity stated are based on worst case analysis, where $|\mathbb{O}|$ is the size of object, $|T|$ is the maximum size of timestamps among all trajectories.}
\label{tbl:existing_co_patterns}
\end{table}

%of densely connected objects that travel together for at least $k$ consecutive time. A \emph{swarm}~\cite{li2010swarm} relax the consecutiveness of \emph{convoy}.
% 
%To formally define the pattern, the temporal dimension of trajectories is descritized into snapshots, where each snapshot contains the geographical information of all moving objects. 
%Given a member size constraint $n$, a temporal constraint $k$, a \emph{co-movement} pattern finds a cluster of objects with at least size $n$ and close in spatial proximity for at least $k$ snapshots. 
%Recently, there have been several works extending the basic pattern to incorporate more advanced temporal constraints. For instance, Jeung et al. proposed \emph{convoy} pattern, which requires the snapshots to be consecutive; Li et al. proposed \emph{swarm} pattern, which relaxes the consecutiveness of snapshots and Li et al. proposed \emph{platoon} pattern which imposed a \emph{minimum local length} on the snapshots. 
%PLEASE BE MORE SPECIFIC FOR THE THREE PATTERNS. ALSO, ADD THE CITATIONS.
\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{related_work.eps}
\caption{Trajectories and co-movement patterns; The example consists of six trajectories across six snapshots. The
clusters of objects in each snapshots are denoted using dotted circles.}
\label{fig:related_work}
\end{figure}

@@

We illustrate these co-movement patterns in Figure~\ref{fig:related_work} with an example of six trajectories.
The temporal dimension is discretized into six snapshots. 
In each snapshot, the objects are clustered as shown in the dotted circle.
By setting the parameters $M=2, K=3$, we are able to discover \emph{convoy}, \emph{flock}, and \emph{swarm} patterns. 
It is notable that \emph{convoy} and \emph{flock} have the same result pattern, this is because both patterns share 
the same constraints on the time duration. 
\emph{Swarm} pattern results in a super set of \emph{convoy} and \emph{flock} patterns, as it 
does not require any consecutiveness on the time duration. By setting $L=2$, we find three \emph{group} patterns. 
If further set $M=2,K=3$, two \emph{platoon} patterns are found. It is observable that the pattern $\{o_5,o_6:1,4,5\} \rangle$ is a \emph{swarm} but is neither a \emph{platoon} nor a \emph{group} since one of its local consecutive duration (i.e. $\{1\}$) is less than $2$. However, $\{o_5,o_6:1,4,5\} \rangle$ can be reduced to $\langle\{o_5,o_6:4,5\} \rangle$ which is a \emph{group} pattern because \emph{group} pattern only restricts the local consecutiveness but not the total size of a duration.

@@

As can be seen, there are various co-movement patterns requested by different applications and it is cumbersome to design a tailored solution for each type. Hence, there is a particular demand for a general platform to support all these co-movement patterns. The other issue with existing methods is that they are built on top of centralized indexes that are not scalable. To the best of our knowledge, the maximum number of trajectories ever evaluated is up to hundreds of thousands of trajectories. In practice, it is rather common to collect at least millions of trajectories and their scalability is left unknown. We, for the first time, evaluate the pattern mining performance at the million scale and report the performance in Figure~\ref{}. The results show that their performance degrades dramatically as the dataset size scales up. In fact, as shown in Table~\ref{tbl:existing_co_patterns}, the mining of co-movement patterns require high complexity. For instance, the
complexities of \emph{swarm} and \emph{platoon} are already exponential. 
Therefore, none of them can handle millions of trajectories efficiently. 
%CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.

Therefore, our primary contributions in this paper are to close these two gaps. First, we propose a general co-movement pattern definition to incorporate all the related variants in the existing literature. We observe that even though \emph{platoon} is the most general pattern among existing patterns, it suffers from \emph{loose connection} problem. 
The \emph{loose connection} problem refers to the patterns that discovered 
are loosely-connected in the temporal domain. For example, in Figure~\ref{fig:platoon_weakpoint}, two objects $o_1, o_2$ 
would form a \emph{platoon} pattern $\{o_1,o_2:1,2,3, 102,103,104\}$. However, the consecutive segment on the pattern's 
duration is $98$ timestamps apart, making the co-movement behavior very weak.
%
%
%%This is because that \emph{platoon} allows the timestamps in a pattern duration to be in arbitrary distance, making the object group loosely
%connected. For instance, patterns with duration $\{1,2,100,101\}$ could be a valid \emph{platoon}; however, the two timestamps $2,100$ are too far from each other.
In reality, such a pattern is likely to be induced by periodic movements of unrelated objects such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc. To cope with this anomaly, we propose the \emph{general co-movement pattern} by introducing the gap parameter $G$, which requires the distance of timestamps in the duration to be no larger than $G$. By so doing, we gain a fine-grained control over the pattern duration, which alleviates the \emph{loose connection} problem. Meanwhile, the general co-movement pattern does not concede its expressiveness. As we show in later sections, the general co-movement pattern is able to express existing patterns by setting appropriate parameters. 
%IS IT POSSIBLE TO USE FIGURE 1 TO ADDRESS THE PROBLEM OF PLATOON, INSTEAD OF PROPOSING A NEW EXAMPLE SCENARIO?

%
\begin{figure}[h]
\center
\includegraphics[width=0.45\textwidth]{platoon_weakpoint.eps}
\caption{Loosely connected pattern in platoon and swarm. The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is included in platoon and swarm results.}
\label{fig:platoon_weakpoint}
\end{figure}

Second, we propose a parallel solution based on modern MapReduce platform for scalable pattern mining. Our
solution is a three-step MapReduce alike approach. First, trajectories are partitioned
into snapshots where clusters from each snapshots are formed in parallel. Second, 
clusters at various timestamps are shuffled and regrouped. Third, the general co-movement patterns
are mined from each group. The challenge here is to ensure that
the patterns mined at step three is complete. If not, further shuffles and computations are required which 
significantly drag down the system performance. In order to resolve the challenges and meanwhile keep the 
shuffle amount at each stage to a minimum, 
we design a novel star-based partition scheme to efficiently partition objects based on their
belonging clusters. Based on the star partition, we then propose a series of optimization techniques which
largely improve the system performance. NEED TO EMPHASIZE YOUR TECHNICAL CONTRIBUTION!

Third, we conduct a set of extensive experiments on XXX datasets with million-scale trajectories. The results show that XXX.

>>>>

A crucial task of data analysis on top of trajectories is 
to discover co-moving patterns. A \emph{co-movement} pattern~\cite{li2013managing} 
refers to a group of objects traveling together for a certain period of time 
and the group is normally determined by spatial proximity. 
A pattern is prominent if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$ are parameters specified by users. Rooted from such basic definition 
and driven by different mining applications, there are a bunch of variants 
of co-movement patterns that have been developed with more advanced constraints.

Table~\ref{tbl:existing_co_patterns} summarizes several popular co-moving patterns 
with different constraints in the attributes of clustering in spatial proximity,
consecutiveness in temporal duration and computational complexity. 
In particular,  the \emph{flock}~\cite{gudmundsson2006flock} 
and \emph{group}~\cite{wang2006grouppattern} patterns require 
all the objects in a group to be enclosed by a disk with radius $r$; 
whereas the \emph{convoy}~\cite{jeung2008convoy}, \emph{swarm}~\cite{li2010swarm} 
and \emph{platoon}~\cite{li2015platoon} patterns resort to density-based 
spatial clustering. 
In the temporal dimension, \emph{flock}~\cite{gudmundsson2006flock} 
and \emph{convoy}~\cite{jeung2008convoy} require all the timestamps 
of each detected spatial group to be consecutive, which is referred to as \emph{global consecutiveness}; 
whereas \emph{swarm}~\cite{li2010swarm} does not impose any restriction. 
The \emph{group}~\cite{wang2006grouppattern} and \emph{platoon}~\cite{li2015platoon} adopt a compromised manner by allowing
arbitrary gaps between the consecutive segments, which is called \emph{local consecutiveness}. 
They introduce a parameter $L$ to control the minimum length of each local consecutive segment.

@@

\begin{table} \scriptsize
\centering
\begin{tabular}{|c|c|c|c|}
\hline 
 & Proximity & Consecutiveness &  Time Complexity\\ 
\hline 
flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||\mathbb{T}|^2 + |\mathbb{O}|log(|\mathbb{O}|))$ \\ 
\hline 
convoy~\cite{jeung2008convoy} & density-based &   global & $O(|\mathbb{O}|^2+|\mathbb{O}||\mathbb{T}|)$\\ 
\hline 
group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|\mathbb{T}|)$ \\ 
\hline 
platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$\\ 
\hline 
swarm~\cite{li2010swarm} & density-based  & no constraint & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$  \\ 
\hline 
\end{tabular} 
\caption{Constraints and complexity of co-movement patterns. The time complexity indicates the performance in the worst case, where $|\mathbb{O}|$ is the total number of objects and $|\mathbb{T}|$ is the number of descritized timestamps.}
\label{tbl:existing_co_patterns}
\end{table}

%of densely connected objects that travel together for at least $k$ consecutive time. A \emph{swarm}~\cite{li2010swarm} relax the consecutiveness of \emph{convoy}.
% 
%To formally define the pattern, the temporal dimension of trajectories is descritized into snapshots, where each snapshot contains the geographical information of all moving objects. 
%Given a member size constraint $n$, a temporal constraint $k$, a \emph{co-movement} pattern finds a cluster of objects with at least size $n$ and close in spatial proximity for at least $k$ snapshots. 
%Recently, there have been several works extending the basic pattern to incorporate more advanced temporal constraints. For instance, Jeung et al. proposed \emph{convoy} pattern, which requires the snapshots to be consecutive; Li et al. proposed \emph{swarm} pattern, which relaxes the consecutiveness of snapshots and Li et al. proposed \emph{platoon} pattern which imposed a \emph{minimum local length} on the snapshots. 
%PLEASE BE MORE SPECIFIC FOR THE THREE PATTERNS. ALSO, ADD THE CITATIONS.
\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{related_work.eps}
\caption{Trajectories and co-movement patterns; The example consists of six trajectories across six snapshots. The
clusters of objects in each snapshots are denoted using dotted circles. Each type of pattern has its parameters. 
$M$ denotes the minimum size of objects.
$K$ denotes the minimum size of timestamps.
$L$ denotes the minimum size of locally consecutive timestamps.}
\label{fig:related_work}
\end{figure}

@@

To better illustrate the temporal constraints of these 
co-movement patterns, we design a scenario with six example trajectories in Figure~\ref{fig:related_work}.
In the setting, the temporal dimension  is discretized into six snapshots. 
In each snapshot, objects are clustered as shown in the dotted circles. We use $M$ to denote
the minimum size of a object group, $K$ to denote the minimum number 
of timestamps in a duration, $L$ to denote the minimum size of local-consecutive segments in a duration.

\noindent\textbf{Global consecutiveness}: \emph{Flock} and \emph{convoy} patterns enforce the pattern duration to be \emph{global consecutive}. We discover one \emph{flock} and one \emph{convoy} pattern, which both correspond to $\{o_3,o_4:1,2,3\}$. It can be verified that no other object groups appears in more than three consecutive timestamps.

\noindent\textbf{Local consecutiveness}: \emph{Group} and \emph{platoon} patterns require the duration to be \emph{locally consecutive}. When setting $L = 2$,
we observe three \emph{group} patterns and three \emph{platoon} patterns. Specifically, \emph{group} aims to find the
pattern with maximal object set whose duration conforms to $L$ consecutiveness. Taking the pattern $\{o_3,o_4,o_5:2,3\}$ as an example. $\{o_3,o_4,o_5\}$ is indeed maximal. If another object, say $o_2$, is added to the group, the duration reduces to $\{3\}$ which is not $L$-consecutive. In fact, adding any other object to this group invalidates the $L$-consecutiveness. In contrary, \emph{platoon} finds the maximal object set whose duration is not only $L$-consecutive but also with size no less than $K$. Therefore, \emph{platoon} finds a different set of patterns. For example, $\{o_4,o_5:2,3,5,6\}$ is a \emph{platoon} pattern but not a \emph{group} pattern. This is because the object set $\{o_4,o_5\}$ is not maximal wrt. \emph{group}, as we can see that adding $o_3$ to the object set results in a larger \emph{group} pattern. Therefore, $\{o_4,o_5:2,3,5,6\}$ is not a \emph{group}.

\noindent\textbf{No consecutiveness}: \emph{Swarm} pattern relaxes the consecutiveness in the duration. Thus as shown in the Figure, \emph{swarm} discover the most number of patterns. In particular, given the same $M$ and $K$, \emph{swarm} result covers all patterns discovered in \emph{flock}, \emph{convoy} and \emph{platoon}. Furthermore, it finds more patterns that are not covered by \emph{flock}, \emph{convoy} and \emph{platoon}. For instance, $\{o_5,o_6, 1,4,5\}$ is a \emph{swarm} but is neither a \emph{platoon} (with $L=2$) nor a \emph{convoy}.

%Therefore, patterns $\{o_1,o_2:1,2,4,5\}$,
%$\{o_3,o_4,o_5:2,3\}$ and $\{o_5,o_6,4,5\}$ are found. Taking

%We illustrate these co-movement patterns in Figure~\ref{fig:related_work} with an example of six trajectories.
%The temporal dimension is discretized into six snapshots. 
%In each snapshot, the objects are clustered as shown in the dotted circle.
%By setting $M=2, K=3$, we are able to discover \emph{convoy}, \emph{flock}, and \emph{swarm} patterns. 
%\emph{Convoy} pattern finds the objects that travels in consecutive timestamps. Only one object group $\{o_3,o_4\}$
%matches the criteria with the timestamps $\{1,2,3\}$. Since the example treats the clusters as given, \emph{flock}
%shares the same pattern result \emph{convoy}.  When the consecutiveness constraint is relax, we discover more patterns.
%By setting $L = 2$, we find three \emph{group} patterns. For example $\{o_1,o_2\}$ forms a \emph{group} pattern
%since they appear together in $\{1,2,4,5\}$, where the local consecutiveness of size $2$ ($L = 2$) is met.

%It is worth noting that \emph{convoy} and \emph{flock} have the same result pattern because both patterns share 
%the same constraints on the time duration. I DON'T UNDERSTAND WHY YOU EMPHASIZE THIS. WHEN WILL THEY BE DIFFERENT?
%The groups detected by \emph{Swarm} are superset of \emph{convoy} and \emph{flock} patterns, as \emph{Swarm} imposes no constraint on temporal consecutiveness. By setting $L=2$, we find three \emph{group} patterns. 
%If further set $M=2,K=3$, two \emph{platoon} patterns are found. It is observable that the pattern $\{o_5,o_6:1,4,5\} \rangle$ is a \emph{swarm} but is neither a \emph{platoon} nor a \emph{group} since one of its local consecutive duration (i.e. $\{1\}$) is less than $2$. However, $\{o_5,o_6:1,4,5\} \rangle$ can be reduced to $\langle\{o_5,o_6:4,5\} \rangle$ which is a \emph{group} pattern because \emph{group} pattern only restricts the local consecutiveness but not the total size of a duration. TOO UGLY! NEED TO EXPLAIN THE FIGURE BASED ON TABLE $1$. AT LEAST READERS CAN HAVE A ROUGH IDEA HOW YOU OBTAIN THE RESULT GROUPS.

@@

As can be seen, there are various co-movement patterns requested by different applications and it is cumbersome to design a tailored solution for each type. 
%Besides, we observe that, the number of co-movement patterns could be nearly exponential. 
%For instance, in the small example in Figure~\ref{fig:related_work}, \emph{swarm} already discovers 5 patterns.
We further identify that existing patterns either miss out interesting patterns (i.e, \emph{convoy}) 
or likely contain non-interesting patterns (i.e., \emph{swarm}, \emph{platoon}).
Hence, there is a particular demand for a new pattern model to fine control the pattern result without losing expressiveness. 
The other issue with existing methods is that they are built on top of centralized indexes that are not scalable. To the best of our knowledge, the maximum number of trajectories ever evaluated is up to hundreds of thousands of trajectories. In practice, it is rather common to collect at least millions of trajectories and their scalability is left unknown. We conduct a theoretical analysis on the worst-case complexity (as listed in Table~\ref{tbl:existing_co_patterns} as well as an experimental evaluation with million-scale cardinality of a trajectory database (as shown in Figure~\ref{}). Results show that their performances degrade dramatically as the dataset size scales up and none of the existing solutions is scalable to handle large-scale trajectories.
%In fact, as shown in Table~, the mining of co-movement patterns require high complexity. For instance, the
%complexities of \emph{swarm} and \emph{platoon} are already exponential. 
%Therefore, none of them can handle millions of trajectories efficiently. 
%CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.

Therefore, our primary contributions in this paper are to close these two gaps. 
First, we summarize two anomalies from existing patterns, namely, \emph{missing-pattern} and \emph{loose-connection}.
The \emph{missing-pattern}~\cite{li2010swarm} anomaly arises due to the stringent constraints on the duration of a pattern. As shown in 
Figure~\ref{fig:platoon_weakpoint} (a). if the duration size is set to be $K=4$, neither \emph{flock}s nor \emph{convoy}s
can be discovered. As we notice, object $o_1$ is temporally far from $o_2$ at timestamp $4$, which is likely to be
the result of errors in interpretation of missing points, or $o_1$ faces traffic control at time $4$. Such an anomaly can
be resolved by \emph{swarm} and \emph{platoon} due to a relaxed constraint on the duration. However, 
\emph{swarm} and \emph{platoon}'s relaxations encompass a type of non-interesting patterns which is referred
as \emph{loose-connection}~\cite{li2015platoon} anomaly. As shown in Figure~\ref{fig:platoon_weakpoint} (b),
the two objects $o_1, o_2$ 
would form a \emph{platoon} pattern $\{o_1,o_2:1,2,3, 102,103,104\}$. However, the consecutive segment on the pattern's 
duration is $98$ timestamps apart, making the co-movement behavior very weak.
%
%
%%This is because that \emph{platoon} allows the timestamps in a pattern duration to be in arbitrary distance, making the object group loosely
%connected. For instance, patterns with duration $\{1,2,100,101\}$ could be a valid \emph{platoon}; however, the two timestamps $2,100$ are too far from each other.
In reality, such a pattern is likely to be induced by periodic movements of unrelated objects such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc. In current literature,
users are unable to explicitly exclude the loosely-connected patterns even when those patterns are unwanted.
%When such loosely-connected patterns are unwanted, users currently are unable to directly control the outputs.
To cope with both of the two anomalies, we propose the \emph{general co-movement pattern} 
by introducing the gap parameter $G$, which requires the distance of 
timestamps in the duration to be no larger than $G$. 
By so doing, we gain a fine-grained control over the pattern duration, which alleviates both the \emph{missing-pattern} and the \emph{loose connection} problem. Meanwhile, the general co-movement pattern does not concede its expressiveness. As we show in later sections, the general co-movement pattern is able to express existing patterns by setting appropriate parameters. Therefore, users are still able to exclude non-consecutive patterns 
or include loosely-connected patterns when they feel necessary.
%IS IT POSSIBLE TO USE FIGURE 1 TO ADDRESS THE PROBLEM OF PLATOON, INSTEAD OF PROPOSING A NEW EXAMPLE SCENARIO?

%
\begin{figure}[h]
\center
\includegraphics[width=0.4\textwidth]{platoon_weakpoint.eps}
\caption{Two anomalies in existing patterns. (a) \emph{Missing-pattern} anomaly
in \emph{flock} and \emph{convoy}. When $K=4$, none of the two patterns can be discovered. (b) \emph{Loose-connection} anomaly in \emph{platoon} and \emph{swarm}. The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is included in platoon and swarm results.}
\label{fig:platoon_weakpoint}
\end{figure}

Second, we propose a parallel solution on modern MapReduce platforms for scalable pattern mining.
The major challenge in designing MapReduce-based algorithms is to make proper partitions of input data.
In GCMP mining, we enforce both the \emph{soundness} and the \emph{completeness} 
of the partitions. Such properties ensure that neither false-patterns 
nor miss-patterns are possible in our solution. To meet such partition requirements
as well as to keep the shuffle amount to a minimum,
% 
%%Second, we propose a . Our
%%solution is a three-step MapReduce alike approach. First, trajectories are partitioned
%%into snapshots where clusters from each snapshots are formed in parallel. Second, 
%%clusters at various timestamps are shuffled and regrouped. Third, the general co-movement patterns
%%are mined from each group. 
%
%The challenge here is to ensure that
%the patterns mined at step three is complete. If not, further shuffles and computations are required which 
%significantly drag down the system performance. In order to resolve the challenges and meanwhile keep the 
%shuffle amount at each stage to a minimum, 
we first design a naive \emph{Temporal Replication and Mining} (TRM)
approach, which partitions trajectories into groups of consecutive snapshots. Then, we design a line-sweep
method for mining GCMP from each partition. We prove that in TRM, the partition is complete and sound when a snapshot is replicated $O(|T|)$ times. 
Then, we design a novel \emph{Star Partition and Mining} (SRM) approach which significantly reduces the data shuffled
as compare to TRM. In SRM, we design a conceptual connection graph based on proximity among objects. We adapt
a \emph{star partition} which cut the graph by replicating vertices. Afterwards, we design an Apriori-like method to mine
GCMP in each partition. We prove the correctness of SPM and show that total data been replicated is $O(|\mathbb{O}|)$.
Moreover, we utilize \emph{temporal monotonicity} in GCMP to further reduce the shuffling and mining cost in SPM. Lastly, we adapt various engineering level techniques to support efficiently deploying our algorithms in 
Apache Spark which is one of the most popular MapReduce platforms.

%we design a novel star-based partition scheme to efficiently partition objects based on their
%belonging clusters. Based on the star partition, we then propose a series of optimization techniques which
%largely improve the system performance. NEED TO EMPHASIZE YOUR TECHNICAL CONTRIBUTION!

We conduct a set of extensive experiments on XXX datasets with million-scale trajectories. The results show that XXX.

### 2016-05-09 sec3_definitions.tex
Further edits on Sec1 and sec4

It is also observable that the number of patterns in GCMP is exponential. To reduce the size of output, 
we notice that, for two patterns $P_1,P_2$, if $P_1.O \subseteq P_2.O$ and $P_2$ is a proper pattern, then $P_1$ is also a proper pattern. Therefore, we can define the \emph{Closed General Co-Movement Pattern} as follows:

@@

For example, let $M=2,K=2,,L=1,G=1$. In Figure~\ref{fig:related_work},
the pattern $P_1 = \{o_3,o_4:1,2,3\}$ is not a closed pattern. This is because $P_2=\{o_3,o_4,o_5:2,3\}$ is a closed pattern and $P_2.O \supset P_1.O$. The closed pattern avoids outputting duplicate information, thus making the result patterns more compact.

LETS KEEP THE CLOSED INFORMATION AT THE MOMENT. IF NO CLOSED IS DEFINED, WE CANNOT REDUCE GCMP TO OTHER PATTERNS SINCE THOSE PATTERNS ARE ALL DEFINED AS ``CLOSED''
%For example, let $n=2,k=2,l=1,g=1$, the pattern $\{o_3,o_4\} \{1,2,3\}$ in Figure~\ref{fig:related_work} is not a closed pattern, while $\{o_3, o_4\} \{t_1,t_2,t_3\}$ is a closed pattern.

@@

\begin{table}[h]
\centering
\begin{tabular}{|c|l|} 
\hline
Symbols & Meanings \\
\hline 
$Tr_i$ & Trajectory of object $i$\\ 
\hline
$S_t$ & Snapshot of objects at time $t$ \\
\hline 
$\mathbb{O}$ & Set of objects \\ 
\hline 
$K$ & Duration constraint\\
\hline
$M$ & Object size constraint \\
\hline
$L$ & Consecutiveness constraint\\
\hline
$G$ & Connection constraint \\
\hline
$T$ & Time sequence \\
\hline
$C_t(o)$ & the cluster of object $o$ at time $t$ \\
\hline 
$Sr_i $ &  The star structure of object $i$ \\
\hline 
\end{tabular} 
\caption{Notions that will be used}
\end{table}

>>>>

It is also observable that the number of patterns in GCMP could be exponential under some parameter settings (i.e., 
when expressing \emph{swarm}). In particular, given a parameter $M$, if a pattern $P$ is valid, then any subset of $P$ with 
size $M$ is also a valid pattern. This results in additional $\Sigma_{M\geq i \geq |P.O|} {|P.O| \choose i}$ patterns,
which is clearly overwhelming and redundant. For all these patterns, output $P$ is sufficient. Therefore, we define the \emph{Closed General Co-Movement Pattern} as follows:
%
%To reduce the size of output, 
%we notice that, for two patterns $P_1,P_2$, if $P_1.O \subseteq P_2.O$ and $P_2$ is a proper pattern, then $P_1$ is also a proper pattern.

@@

For example, let $M=2,K=2,,L=1,G=1$. In Figure~\ref{fig:related_work},
the pattern $P_1 = \{o_3,o_4:1,2,3\}$ is not a closed pattern. This is because $P_2=\{o_3,o_4,o_5:2,3\}$ is a closed pattern since $P_2.O \supset P_1.O$. The closed pattern avoids outputting duplicate information, thus making the result patterns more compact. 
%LETS KEEP THE CLOSED INFORMATION AT THE MOMENT. IF NO CLOSED IS DEFINED, WE CANNOT REDUCE GCMP TO OTHER PATTERNS SINCE THOSE PATTERNS ARE ALL DEFINED AS ``CLOSED''
%For example, let $n=2,k=2,l=1,g=1$, the pattern $\{o_3,o_4\} \{1,2,3\}$ in Figure~\ref{fig:related_work} is not a closed pattern, while $\{o_3, o_4\} \{t_1,t_2,t_3\}$ is a closed pattern.

@@

\begin{table}[h]
\centering
\begin{tabular}{|c|l|} 
\hline
Symbols & Meanings \\
\hline 
$Tr_i$ & Trajectory of object $i$\\ 
\hline
$S_t$ & Snapshot of objects at time $t$ \\
\hline 
$\mathbb{O}$ & Set of objects \\ 
\hline
$M$ & Object size constraint \\
\hline 
$K$ & Duration constraint\\
\hline
$L$ & Consecutiveness constraint\\
\hline
$G$ & Connection constraint \\
\hline
$T$ & Time sequence \\
\hline
$C_t(o)$ & the cluster of object $o$ at time $t$ \\
\hline 
$Sr_i $ &  The star structure of object $i$ \\
\hline 
\end{tabular} 
\caption{Notions that will be used}
\end{table}
